% !TeX program = pdflatex
\documentclass[letterpaper,10pt]{article}

% --- Packages ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.75in]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{array}
\usepackage{ragged2e}

% --- Colors ---
\definecolor{linkcolor}{rgb}{0,0.2549,0.5686}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=linkcolor,
    citecolor=linkcolor
}

% --- Section Style ---
\titleformat{\section}
  {\large\scshape\raggedright}
  {}{0em}
  {}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{3pt}

% --- Spacing ---
\newcommand{\blankline}{\vspace{1em}}
\pagestyle{plain}
\setlength{\parskip}{0.5em}
\setlist[enumerate]{leftmargin=*, itemsep=2pt, topsep=4pt}

% --- Begin Document ---
\begin{document}

%----------------------------------------------------------------------------------------
% HEADER
%----------------------------------------------------------------------------------------

\begin{center}
    {\huge \textbf{Muhammad Wasif Zafar, Ph.D.}} \\[0.5em]
    {\large
        Assistant Professor, \\
        \href{https://lhr.nu.edu.pk/}{FAST School of Management}, \\
        \href{https://nu.edu.pk/}{National University of Computer and Emerging Sciences (NUCES)}, Lahore, Pakistan
    } \\[1em]
    \begin{tabular}{@{}l@{ }l@{ }l@{}}
        House \#332, B Block, PUEHS & \textsc{Phone:} & +92 346 756 8266 \\
        Lahore, Punjab, Pakistan     & \textsc{Email:} & \href{mailto:wasif.zafar6@yahoo.com}{wasif.zafar6@yahoo.com} \\
                                     & \textsc{ORCID:} & \href{https://orcid.org/0000-0001-5790-3196}{orcid.org/0000-0001-5790-3196}
    \end{tabular}
\end{center}

\blankline

%----------------------------------------------------------------------------------------
% RESEARCH INTERESTS
%----------------------------------------------------------------------------------------

\section{Research Interests}
Green Finance, Sustainability, Energy Economics, Capital Markets.

\blankline

%----------------------------------------------------------------------------------------
% EMPLOYMENT
%----------------------------------------------------------------------------------------

\section{Employment}

\begin{tabular}{@{}p{10.5cm} r}
    \textbf{Assistant Professor} & \textsc{Jan 2025 -- Present} \\
    \href{https://lhr.nu.edu.pk/}{FAST School of Management}, \href{https://nu.edu.pk/}{NUCES}, Lahore, Pakistan & \\
\end{tabular}

\begin{tabular}{@{}p{10.5cm} r}
    \textbf{Assistant Professor} & \textsc{Mar 2022 -- Present} \\
    \href{http://www.riphah.edu.pk}{Riphah School of Business Management}, \href{http://www.riphah.edu.pk}{Riphah International University}, Lahore, Pakistan & \\
\end{tabular}

\begin{tabular}{@{}p{10.5cm} r}
    \textbf{Postdoc Fellow} & \textsc{Nov 2019 -- Oct 2021} \\
    College of Management, \href{http://www.szu.edu.cn}{Shenzhen University}, China (AACSB, EMBA, Equis) & \\
\end{tabular}

\begin{tabular}{@{}p{10.5cm} r}
    \textbf{Lecturer} & \textsc{Jan 2014 -- Jun 2021} \\
    Department of Management Sciences, \href{http://www.comsats.edu.pk}{COMSATS University Islamabad}, Pakistan & \\
\end{tabular}

\blankline

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{tabular}{@{}r @{ } p{12cm}@{}}
    2015--2019 & Ph.D. in \textsc{Management Science and Engineering} (Finance and Economics) \\
               & \href{http://www.bit.edu.cn}{Beijing Institute of Technology}, China \\
               & (QS ranked 302; AACSB, EMBA, Equis) \\[0.5em]
    2010--2012 & Master of Science in \textsc{Management Science} (Finance) \\
               & \href{http://www.comsats.edu.pk}{COMSATS University Islamabad}, Pakistan \\[0.5em]
    2005--2009 & Bachelor of Commerce (Hons) in \textsc{MSIT} \\
               & \href{http://www.iub.edu.pk}{The Islamia University of Bahawalpur}, Pakistan \\
\end{tabular}

\blankline

%----------------------------------------------------------------------------------------
% ACHIEVEMENTS
%----------------------------------------------------------------------------------------

\section{Achievements}
\textbf{Top 2\% Scientists Worldwide 2025} (Stanford University)\\[4pt]
\textbf{Associate Editor:} \textit{Environment, Development and Sustainability} (IF 4.7)

\blankline

%----------------------------------------------------------------------------------------
% RESEARCH IMPACT
%----------------------------------------------------------------------------------------

\section{Research Impact Summary}
\begin{tabular}{@{}r l@{}}
    \textbf{ORCID:} & \href{https://orcid.org/0000-0001-5790-3196}{orcid.org/0000-0001-5790-3196} \\
    \textbf{Total IF:} & 470 \\
    \textbf{h-index (2025):} & 39 \\
    \textbf{i10-index (2025):} & 57 \\
    \textbf{Citations (2025):} & 9,441 \\
\end{tabular}

\blankline

%----------------------------------------------------------------------------------------
% PUBLICATIONS
%----------------------------------------------------------------------------------------

\section{Publications}

\begin{enumerate}[leftmargin=0.5cm]

\item \textbf{Unriddling the Environmental Implications of Energy Resources, Globalization, Biocapacity, and Open Trading: Does Human Capital Provoke a Change in Emerging 7?} \\
      Satrovic, Elma, Irfan Khan, \textbf{Muhammad Wasif Zafar} \\
      \textit{Environmental Modeling \& Assessment}, 2025. \textbf{SCI} \\
      \href{https://doi.org/10.1007/s10666-025-10055-9}{DOI}

\item \textbf{Gold and cryptos in multi-asset portfolios: time-frequency dynamics.} \\
      Ramzan, Shahzad, Mian Muhammad Atif, \textbf{Muhammad Wasif Zafar} \\
      \textit{Applied Economics Letters}, 2025. \textbf{SSCI}

\item \textbf{Does Financial Inclusion Enhance Energy Efficiency? Moderating Roles of Education and Foreign Direct Investment.} \\
      Tian, Guixian, \textbf{Muhammad Wasif Zafar}, Avik Sinha, Mehmet Akif Destek \\
      \textit{Social Indicators Research}, 2025. \textbf{SSCI}

\item \textbf{Unveiling the synergy: How natural resources, energy prices and financial development drive the energy transition in N-11 countries.} \\
      Zhou, A., Zhang, X., Li, W., \textbf{Zafar, M.W.} \\
      \textit{Review of Development Economics}, 2025. \textbf{SSCI} \\
      \href{https://doi.org/10.1111/rode.13138}{DOI}

\item \textbf{The Role of Audit Quality in Waste Management Behavior.} \\
      Saeed, A., \textbf{Zafar, M.W.}, Manita, R., Zahid, N. \\
      \textit{International Review of Economics and Finance}, 2024. \textbf{SSCI} \\
      \href{https://doi.org/10.1016/j.iref.2023.08.019}{DOI}

\item \textbf{COP 28 Policy Perspectives: Achieving Environmental Sustainability through FDI, Technological Innovation Index, Trade Openness, Energy Consumption, and Economic Development in N-11 Emerging Economies.} \\
      Abbass, K., \textbf{Zafar, M.W.}, et al. \\
      \textit{Journal of Environmental Management}, 2024. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.jenvman.2024.122271}{DOI}

\item \textbf{Promoting Sustainability in Developing Countries: A Machine Learning-Based Approach...} \\
      Ahmad Khan, K., Anser, M.K., Pala, F., Barut, A., \textbf{Zafar, M.W.} \\
      \textit{Gondwana Research}, 2024. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.gr.2024.03.013}{DOI}

\item \textbf{Achieving Ecological Sustainability in European Union: The Role of Fiscal Decentralization and Green Innovation.} \\
      Satrovic, E., \textbf{Zafar, M.W.}, Suntraruk, P. \\
      \textit{Journal of Cleaner Production}, 2024. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.jclepro.2024.141316}{DOI}

\item \textbf{Fostering Green Progress: The Dual Influence of Natural Resource Rent and Human Capital...} \\
      Jin, D., \textbf{Zafar, M.W.} \\
      \textit{Natural Resources Forum}, 2024. \textbf{SSCI} \\
      \href{https://doi.org/10.1111/1477-8947.12405}{DOI}

\item \textbf{Greening the Energy Future: Role of Energy Innovation as Policy Driver.} \\
      Sheng, J., Sinha, A., Mansoor, S., \textbf{Zafar, M.W.} \\
      \textit{Natural Resources Forum}, 2024. \textbf{SSCI} \\
      \href{https://doi.org/10.1111/1477-8947.12426}{DOI}

% --- Continue with remaining 52 publications (full list below) ---
% --- Paste from here ---

\item \textbf{Internalizing Negative Environmental Externalities through Environmental Technologies...} \\
      Zhu, S., Wasif, M., Usman, M., Kalugina, O.A. \\
      \textit{Sustainable Energy Technologies and Assessments}, 2024. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.seta.2024.103726}{DOI}

\item \textbf{Information Communication Technology, Globalization, and Energy Poverty...} \\
      Wang, C., Pan, X., Wang, D., \textbf{Zafar, M.W.} \\
      \textit{Sustainable Development}, 2024. \textbf{SSCI} \\
      \href{https://doi.org/10.1002/sd.3077}{DOI}

\item \textbf{An Assessment of Energy Poverty in Sub-Saharan Africa...} \\
      Wang, H., \textbf{Zafar, M.W.}, Abbas, S., Destek, M.A. \\
      \textit{Economic Change and Restructuring}, 2023. \textbf{SSCI} \\
      \href{https://doi.org/10.1007/s10644-023-09568-8}{DOI}

\item \textbf{Capital Flow and Environmental Quality at Crossroads...} \\
      Destek, M.A., Sinha, A., Ozsoy, F.N., \textbf{Zafar, M.W.} \\
      \textit{Environmental Science and Pollution Research}, 2023. \textbf{SCI} \\
      \href{https://doi.org/10.1007/s11356-023-27794-5}{DOI}

\item \textbf{Sustainable Energy Policy, Socio-Economic Development...} \\
      Jie, H., Khan, I., Alharthi, M., \textbf{Zafar, M.W.}, Saeed, A. \\
      \textit{Utilities Policy}, 2023. \textbf{SSCI} \\
      \href{https://doi.org/10.1016/j.jup.2023.101490}{DOI}

\item \textbf{Do Oil and Natural Gas Prices Affect Carbon Efficiency...} \\
      Liu, H., Pata, U.K., \textbf{Zafar, M.W.}, et al. \\
      \textit{Resources Policy}, 2023. \textbf{SSCI} \\
      \href{https://doi.org/10.1016/j.resourpol.2023.104039}{DOI}

\item \textbf{The Path to Sustainable Environment: Do Environmental Taxes and Governance Matter?} \\
      Liu, H., \textbf{Zafar, M.W.}, Sinha, A., Khan, I. \\
      \textit{Sustainable Development}, 2023. \textbf{SSCI} \\
      \href{https://doi.org/10.1002/sd.2505}{DOI}

\item \textbf{Articulating Natural Resource Abundance, Economic Complexity...} \\
      Saud, S., Haseeb, A., \textbf{Zafar, M.W.}, Li, H. \\
      \textit{Resources Policy}, 2023. \textbf{SSCI} \\
      \href{https://doi.org/10.1016/j.resourpol.2022.103261}{DOI}

\item \textbf{Impact of Globalisation, Remittances and Human Capital...} \\
      Yameogo, C.E.W., Mushtaq, R., \textbf{Zafar, M.W.}, et al. \\
      \textit{International Journal of Finance and Economics}, 2023. \textbf{SSCI} \\
      \href{https://doi.org/10.1002/ijfe.2844}{DOI}

\item \textbf{The Transition to Clean Energy and the External Balance...} \\
      Niu, X.Q., Dong, W., Niu, X.D., \textbf{Zafar, M.W.} \\
      \textit{Gondwana Research}, 2023. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.gr.2023.03.003}{DOI}

\item \textbf{Environmental Reverberations of Geopolitical Risk...} \\
      Pata, U.K., Kartal, M.T., Liu, H., \textbf{Zafar, M.W.} \\
      \textit{Environmental Research}, 2023. \textbf{SCI}

\item \textbf{Impact of Energy Efficiency on CO2 Emissions...} \\
      Mehmood Mirza, F., Sinha, A., Khan, J.R., Kalugina, O.A., \textbf{Zafar, M.W.} \\
      \textit{Gondwana Research}, 2022. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.gr.2021.11.017}{DOI}

\item \textbf{Global Perspectives on Environmental Kuznets Curve...} \\
      Anwar, M.A., Shahbaz, M., Zhou, R., \textbf{Zafar, W.} \\
      \textit{Gondwana Research}, 2022. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.gr.2021.11.010}{DOI}

\item \textbf{A Novel Temporal-Spatial Decomposition on Drivers of China’s Carbon Emissions.} \\
      Qin, Q., Yan, H., Li, B., Lv, W., \textbf{Zafar, M.W.} \\
      \textit{Gondwana Research}, 2022. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.gr.2022.05.001}{DOI}

\item \textbf{Environmental Impact of Information and Communication Technology...} \\
      Zhang, C., Khan, I., Dagar, V., Saeed, A., \textbf{Zafar, M.W.} \\
      \textit{Technological Forecasting \& Social Change}, 2022. \textbf{SSCI} \\
      \href{https://doi.org/10.1016/j.techfore.2022.121570}{DOI}

\item \textbf{Assessing Environmental Quality through Natural Resources...} \\
      Zhang, Y., Khan, I., \textbf{Zafar, M.W.} \\
      \textit{Environmental Science and Pollution Research}, 2022. \textbf{SCI} \\
      \href{https://doi.org/10.1007/s11356-022-22005-z}{DOI}

\item \textbf{ICT and Education as Determinants of Environmental Quality...} \\
      \textbf{Zafar, M.W.}, Zaidi, S.A.H., Mansoor, S., Sinha, A., Qin, Q. \\
      \textit{Technological Forecasting \& Social Change}, 2022. \textbf{SSCI} \\
      \href{https://doi.org/10.1016/j.techfore.2022.121547}{DOI}

\item \textbf{Environmental Sustainability in Developing Countries...} \\
      Zhao, F., Zhang, Y., Alharthi, M., \textbf{Zafar, M.W.} \\
      \textit{Sustainable Development}, 2022. \textbf{SSCI} \\
      \href{https://doi.org/10.1002/sd.2350}{DOI}

\item \textbf{The Impact of Digital Finance on the Natural Resource Market...} \\
      Cevik, E.I., Gunay, S., \textbf{Zafar, M.W.}, et al. \\
      \textit{Resources Policy}, 2022. \textbf{SSCI} \\
      \href{https://doi.org/10.1016/j.resourpol.2022.103081}{DOI}

\item \textbf{A Non-Linear Analysis of the Impacts of Natural Resources...} \\
      Liu, H., Alharthi, M., Atil, A., Wasif, M., Khan, I. \\
      \textit{Resources Policy}, 2022. \textbf{SSCI} \\
      \href{https://doi.org/10.1016/j.resourpol.2022.102940}{DOI}

\item \textbf{Analyzing Global Inequality in Access to Energy...} \\
      Sinha, A., Balsalobre-Lorente, D., Wasif, M., Mansoor, M. \\
      \textit{Journal of Environmental Management}, 2022. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.jenvman.2021.114299}{DOI}

\item \textbf{Understanding the Role of Technology in Asian Economies...} \\
      Liu, H., Alharthi, M., \textbf{Zafar, M.W.}, et al. \\
      \textit{Evaluation Review}, 2022. \textbf{SSCI} \\
      \href{https://doi.org/10.1177/0193841X221120483}{DOI}

\item \textbf{Impact of Governance and Globalization on Natural Resources Volatility...} \\
      Liu, H., Al-faryan, M.A.S., Khan, I., Wasif, M. \\
      \textit{Resources Policy}, 2022. \textbf{SSCI} \\
      \href{https://doi.org/10.1016/j.resourpol.2022.102881}{DOI}

\item \textbf{Moving toward Sustainable Development of Sub-Saharan African Countries...} \\
      Liu, H., Sinha, A., Destek, M.A., Alharthi, M., \textbf{Zafar, M.W.} \\
      \textit{Sustainable Development}, 2022. \textbf{SSCI} \\
      \href{https://doi.org/10.1002/sd.2367}{DOI}

\item \textbf{Audit Quality and Corporate Trade Credit...} \\
      Saeed, A., Munir, Z., \textbf{Zafar, M.W.} \\
      \textit{International Journal of Emerging Markets}, 2022. \textbf{SSCI} \\
      \href{https://doi.org/10.1108/IJOEM-06-2022-0903}{DOI}

\item \textbf{Determinants of CO2 Emissions in the BRICS Economies...} \\
      Caglar, A.E., \textbf{Zafar, M.W.}, Bekun, F.V., Mert, M. \\
      \textit{Sustainable Energy Technologies and Assessments}, 2022. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.seta.2021.101907}{DOI}

\item \textbf{Effects of Biomass Energy Consumption on Environmental Quality...} \\
      \textbf{Zafar, M.W.}, Sinha, A., Ahmed, Z., Qin, Q., Zaidi, S.A.H. \\
      \textit{Renewable and Sustainable Energy Reviews}, 2021. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.rser.2021.110868}{DOI}

\item \textbf{The Linkages among Natural Resources, Renewable Energy...} \\
      \textbf{Zafar, M.W.}, Saeed, A., Zaidi, S.A.H., Waheed, A. \\
      \textit{Sustainable Development}, 2021. \textbf{SSCI} \\
      \href{https://doi.org/10.1002/sd.2151}{DOI}

\item \textbf{A Controversy on the Three Fundamental Growth Determinants...} \\
      Yun, H., Shah, L., Haseeb, A., \textbf{Zafar, M.W.}, Chen, S. \\
      \textit{Environmental Science and Pollution Research}, 2021. \textbf{SCI}

\item \textbf{Analyzing the Determinants of Clean Energy Consumption...} \\
      Usman, M., Ma, Z., \textbf{Zafar, M.W.}, Waheed, A., Li, M. \\
      \textit{Environmental Science and Pollution Research}, 2021. \textbf{SCI} \\
      \href{https://doi.org/10.1007/s11356-021-14473-6}{DOI}

\item \textbf{The Dynamic Linkage between Remittances, Export Diversification...} \\
      \textbf{Zafar, M.W.}, Saleem, M.M., Destek, M.A., Caglar, A.E. \\
      \textit{Sustainable Development}, 2021. \textbf{SSCI} \\
      \href{https://doi.org/10.1002/sd.2236}{DOI}

\item \textbf{Linking Urbanization, Human Capital, and the Ecological Footprint...} \\
      Ahmed, Z., Wasif, M., Ali, S. \\
      \textit{Sustainable Cities and Society}, 2020. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.scs.2020.102064}{DOI}

\item \textbf{Analyzing the Association between Innovation, Economic Growth...} \\
      Zameer, H., Yasmeen, H., \textbf{Zafar, M.W.}, Waheed, A., Sinha, A. \\
      \textit{Environmental Science and Pollution Research}, 2020. \textbf{SCI} \\
      \href{https://doi.org/10.1007/s11356-020-09112-5}{DOI}

\item \textbf{Analyzing the Linkage between Military Spending...} \\
      Ahmed, Z., \textbf{Zafar, M.W.}, Mansoor, S. \\
      \textit{Environmental Science and Pollution Research}, 2020. \textbf{SCI} \\
      \href{https://doi.org/10.1007/s11356-020-10076-9}{DOI}

\item \textbf{Determinants of the Ecological Footprint in Thailand...} \\
      Kongbuamai, N., \textbf{Zafar, M.W.}, Zaidi, S.A.H., Liu, Y. \\
      \textit{Environmental Science and Pollution Research}, 2020. \textbf{SCI} \\
      \href{https://doi.org/10.1007/s11356-020-09977-6}{DOI}

\item \textbf{Impact of Green Manufacturing on Consumer Ecological Behavior...} \\
      Waheed, A., Zhang, Q., Rashid, Y., Tahir, M.S., \textbf{Zafar, M.W.} \\
      \textit{Sustainable Development}, 2020. \textbf{SSCI} \\
      \href{https://doi.org/10.1002/sd.2093}{DOI}

\item \textbf{Foreign Direct Investment and Education as Determinants...} \\
      \textbf{Zafar, M.W.}, Qin, Q., Malik, M.N., Zaidi, S.A.H. \\
      \textit{Journal of Environmental Management}, 2020. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.jenvman.2020.110827}{DOI}

\item \textbf{Effects of Diversified Openness Channels...} \\
      Wei, Z., Han, B., Pan, X., Shahbaz, M., \textbf{Zafar, M.W.} \\
      \textit{Energy Economics}, 2020. \textbf{SSCI} \\
      \href{https://doi.org/10.1016/j.eneco.2020.104836}{DOI}

\item \textbf{How Renewable Energy Consumption Contribute to Environmental Quality...} \\
      \textbf{Zafar, M.W.}, Shahbaz, M., Sinha, A., Sengupta, T., Qin, Q. \\
      \textit{Journal of Cleaner Production}, 2020. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.jclepro.2020.122149}{DOI}

\item \textbf{Identification and Analysis of Driving Factors of CO2 Emissions...} \\
      Akram, Z., Engo, J., Akram, U., \textbf{Zafar, M.W.} \\
      \textit{Environmental Science and Pollution Research}, 2019. \textbf{SCI} \\
      \href{https://doi.org/10.1007/s11356-019-05281-0}{DOI}

\item \textbf{The Impact of Natural Resources, Human Capital...} \\
      \textbf{Zafar, M.W.}, Zaidi, S.A.H., Khan, N.R., et al. \\
      \textit{Resources Policy}, 2019. \textbf{SSCI} \\
      \href{https://doi.org/10.1016/j.resourpol.2019.101428}{DOI}

\item \textbf{The Impact of Globalization, Natural Resources Abundance...} \\
      Zaidi, S.A.H., Wei, Z., Gedikli, A., \textbf{Zafar, M.W.}, et al. \\
      \textit{Resources Policy}, 2019. \textbf{SSCI} \\
      \href{https://doi.org/10.1016/j.resourpol.2019.101476}{DOI}

\item \textbf{Dynamic Linkages between Globalization, Financial Development...} \\
      Zaidi, S.A.H., \textbf{Zafar, M.W.}, Shahbaz, M., Hou, F. \\
      \textit{Journal of Cleaner Production}, 2019. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.jclepro.2019.04.210}{DOI}

\item \textbf{Investigation of Energy Consumption–Economic Growth Nexus...} \\
      Erdoğan, S., Gedikli, A., Yılmaz, A.D., Haider, A., \textbf{Zafar, M.W.} \\
      \textit{Energy Reports}, 2019. \textbf{SCI} \\
      \href{https://doi.org/10.1016/j.egyr.2019.08.034}{DOI}

\item \textbf{Are Air Pollution, Economic and Non-Economic Factors...} \\
      Usman, M., Ma, Z., \textbf{Zafar, M.W.}, Haseeb, A., Ashraf, R.U. \\
      \textit{International Journal of Environmental Research and Public Health}, 2019. \textbf{SCI} \\
      \href{https://doi.org/10.3390/ijerph16111967}{DOI}

\item \textbf{From Nonrenewable to Renewable Energy and Its Impact...} \\
      \textbf{Zafar, M.W.}, Shahbaz, M., Hou, F., Sinha, A. \\
      \textit{Journal of Cleaner Production}, 2019. \textbf{SCI}

\item \textbf{The Role of Stock Market and Banking Sector Development...} \\
      \textbf{Zafar, M.W.}, Zaidi, S.A.H., Sinha, A., Gedikli, A., Hou, F. \\
      \textit{Resources Policy}, 2019. \textbf{SSCI} \\
      \href{https://doi.org/10.1016/j.resourpol.2019.05.003}{DOI}

\item \textbf{The Nexus of Renewable and Nonrenewable Energy...} \\
      \textbf{Zafar, M.W.}, Mirza, F.M., Zaidi, S.A.H., Hou, F. \\
      \textit{Environmental Science and Pollution Research}, 2019. \textbf{SCI}

\item \textbf{Determinants of Carbon Emissions in Pakistan’s Transport Sector.} \\
      Rasool, Y., Zaidi, S.A.H., \textbf{Zafar, M.W.} \\
      \textit{Environmental Science and Pollution Research}, 2019. \textbf{SCI}

\item \textbf{Uncovering the Driving Forces of Carbon Dioxide Emissions...} \\
      Shi, Y., Han, B., \textbf{Zafar, M.W.}, Wei, Z. \\
      \textit{Environmental Science and Pollution Research}, 2019. \textbf{SCI}

\item \textbf{From Nonrenewable to Renewable Energy...} \\
      \textbf{Zafar, M.W.}, Shahbaz, M., Hou, F., Sinha, A. \\
      \textit{Journal of Cleaner Production}, 2018. \textbf{SSCI/SCI} \\
      \href{https://doi.org/10.1016/j.jclepro.2018.12.081}{DOI}

\item \textbf{A Novel Method for Multiattribute Decision Making...} \\
      Du, Y., Hou, F., \textbf{Zafar, W.}, Yu, Q., Zhai, Y. \\
      \textit{International Journal of Intelligent Systems}, 2017. \\
      \href{https://doi.org/10.1002/int.21881}{DOI}

\end{enumerate}

\blankline

%----------------------------------------------------------------------------------------
% ACADEMIC RESPONSIBILITIES
%----------------------------------------------------------------------------------------

\section{Academic Responsibilities}
\begin{itemize}
    \item Graduate Research Incharge
    \item Graduate Exam Superintendent
    \item Academic Batch Advisor – BBA
    \item Program Coordinator – B.Com (Hons)
    \item Member, Department Admission Committee
\end{itemize}

\blankline

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------

\section{Data Analysis Skills}
\textbf{Expert:} SAS, STATA, EViews, GAUSS, R

\section{Languages}
Fluent in English, Punjabi, Urdu (native); excellent writing, speaking, presenting, listening in English.

\blankline

%----------------------------------------------------------------------------------------
% PERSONAL
%----------------------------------------------------------------------------------------

\section{Personal Details}
\begin{tabular}{@{}r@{\hspace{1.5em}}l@{}}
  Gender:        & Male \\
  Nationality:   & Pakistani \\
  Date of Birth: & 20 February 1988 \\
\end{tabular}

\end{document}